Overview and Summary of the First Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE1) \note{\scriptsize Authors, please add/check middle initials and affiliations}

### 2014-04-21 WSSSPE1_report/WSSSPE1_summary_report.tex
Removes duplicated word.

In places, Bourne said, development in science has improved thanks to
open source and hosting services like GitHub~\cite{github-web}, but for the most part
remains arcane. He argued that we can learn much from the App Store
model about interfaces, ratings, and so on. He also mentioned
BioJava~\cite{biojava-web} and Open Science Data Cloud~\cite{osdc-web}
as distribution channels.  On a related note, Bourne observed a common
evolutionary pathway for computational biology projects, from data
archive to analytics platform to educational use, and suggested that
use of scientific software for outreach might be the final step.

>>>>

In places, Bourne said, development in science has improved thanks to
open source and hosting services like GitHub~\cite{github-web}, but
for the most part it
remains arcane. He argued that we can learn much from the App Store
model about interfaces, ratings, and so on. He also mentioned
BioJava~\cite{biojava-web} and Open Science Data Cloud~\cite{osdc-web}
as distribution channels.  On a related note, Bourne observed a common
evolutionary pathway for computational biology projects, from data
archive to analytics platform to educational use, and suggested that
use of scientific software for outreach might be the final step.
